Bias no more: A practical guide to latent group-mean centering in longitudinal and other hierarchical bayesian models

### 2022-12-07 ms.Rmd
Draft a motivational paragraph.

# Plotting options
theme_set(
  theme_linedraw(base_size = 9.6) +
    theme(
      strip.background = element_rect(fill = "gray90", color = "gray90"),
      strip.text = element_text(color = "black", hjust = 0),
      panel.grid = element_blank()
    )
)
```

@@

@@

>>>>

# Plotting options
theme_set(
  theme_linedraw(base_size = 10) +
    theme(
      strip.background = element_rect(fill = "gray90", color = "gray90"),
      strip.text = element_text(color = "black", hjust = 0),
      panel.grid = element_blank()
    )
)
```

@@

However, previously latent mean centering has only been available through commercial software packages (MPlus), and was suggested to only apply to latent variables models (M & H). We show a general approach to latent group mean centering using the freely available and flexible R package Bayesian Regression Modelling using Stan (brms; Bürkner), and that latent mean centering applies to *all* analyses of repeated measures (or, generally, clustered) data.

@@

To illustrate latent group-mean centering in practice, we introduce an example dataset of 100 Dutch adolescents, from a study by [@cite].
